Exploring dimensions of biodiversity in Japanese ferns

### 2020-06-30 ms/SI.Rmd
Update SI

>>>>

```{r biplots}

loadd(ses_phy_ferns, cache = ja_fern_cache)
loadd(ses_traits_ferns, cache = ja_fern_cache)
loadd(shape_ferns, cache = ja_fern_cache)

# Helper function for making a scatterplot
scatterplot <- function(data, x_var, y_var, x_lab, y_lab) {
  ggplot(data, aes(x = .data[[x_var]], y = .data[[y_var]])) +
    geom_point(alpha = 0.5) +
    labs(
      x = x_lab,
      y = y_lab
    )
}

# Join data
ses_comp <-
ses_phy_ferns %>%
  select(site, mpd_obs, pe_obs, mpd_obs_z, pe_obs_z) %>%
  left_join(
    select(ses_traits_ferns, site, mpd_morph_obs, mpd_morph_obs_z),
    by = "site"
  ) %>%
  left_join(
    as_tibble(shape_ferns) %>% select(site = grids, richness),
    by = "site"
  )

# Raw metrics ----

# Make dataframe of arguments to feed into plotting function
# - includes all non-duplicated combinations of raw diversity metrics
raw_comparisons <-
  cross_df(
    list(
      x_var = c("mpd_obs", "pe_obs", "mpd_morph_obs", "richness"),
      y_var = c("mpd_obs", "pe_obs", "mpd_morph_obs")
    ),
    .filter = `==` # filter out exact duplicates
  ) %>%
  # Remove reversed duplicates
  # https://stackoverflow.com/questions/22756392/deleting-reversed-duplicates-with-r
  group_by(grp = paste(pmax(x_var, y_var), pmin(x_var, y_var), sep = "_")) %>%
  # Use factors to keep the preferred combination of x and y
  mutate(x_var = as.factor(x_var) %>% fct_relevel("pe_obs", "mpd_morph_obs", "richness")) %>%
  mutate(y_var = as.factor(y_var) %>% fct_relevel("mpd_obs", "pe_obs", "mpd_morph_obs")) %>%
  arrange(x_var, y_var) %>%
  slice(1) %>%
  ungroup() %>%
  select(-grp) %>%
  # Convert x_var and y_var back to character for plotting function
  mutate(across(c(x_var, y_var), as.character)) %>%
  # Add labels
  mutate(
    x_lab = case_when(
      x_var == "mpd_morph_obs" ~ "MMD",
      x_var == "mpd_obs" ~ "MPD",
      x_var == "pe_obs" ~ "PE",
      x_var == "richness" ~ "Richness"
    ),
    y_lab = case_when(
      y_var == "mpd_morph_obs" ~ "MMD",
      y_var == "mpd_obs" ~ "MPD",
      y_var == "pe_obs" ~ "PE",
      y_var == "richness" ~ "Richness"
    )
  )

# Make plot
pmap(raw_comparisons, scatterplot, data = ses_comp) %>%
wrap_plots() +
  plot_annotation(tag_levels = 'A')

# SES metrics ----

# Make dataframe of arguments to feed into plotting function
# - includes all non-duplicated combinations of raw diversity metrics
ses_comparisons <-
  cross_df(
    list(
      x_var = c("mpd_obs_z", "pe_obs_z", "mpd_morph_obs_z", "richness"),
      y_var = c("mpd_obs_z", "pe_obs_z", "mpd_morph_obs_z")
    ),
    .filter = `==` # filter out exact duplicates
  ) %>%
  # Remove reversed duplicates
  # https://stackoverflow.com/questions/22756392/deleting-reversed-duplicates-with-r
  group_by(grp = paste(pmax(x_var, y_var), pmin(x_var, y_var), sep = "_")) %>%
  # Use factors to keep the preferred combination of x and y
  mutate(x_var = as.factor(x_var) %>% fct_relevel("pe_obs_z", "mpd_morph_obs_z", "richness")) %>%
  mutate(y_var = as.factor(y_var) %>% fct_relevel("mpd_obs_z", "pe_obs_z", "mpd_morph_obs_z")) %>%
  arrange(x_var, y_var) %>%
  slice(1) %>%
  ungroup() %>%
  select(-grp) %>%
  # Convert x_var and y_var back to character for plotting function
  mutate(across(c(x_var, y_var), as.character)) %>%
  # Add labels
  mutate(
    x_lab = case_when(
      x_var == "mpd_morph_obs_z" ~ "SES MMD",
      x_var == "mpd_obs_z" ~ "SES MPD",
      x_var == "pe_obs_z" ~ "SES PE",
      x_var == "richness" ~ "Richness"
    ),
    y_lab = case_when(
      y_var == "mpd_morph_obs_z" ~ "SES MMD",
      y_var == "mpd_obs_z" ~ "SES MPD",
      y_var == "pe_obs_z" ~ "SES PE",
      y_var == "richness" ~ "Richness"
    )
  )

# Make plot
pmap(ses_comparisons, scatterplot, data = ses_comp) %>%
  wrap_plots() +
  plot_annotation(tag_levels = 'A')
```
